Analysis PPM-S

### 2020-06-10 production/prod_analysis-cfa.rmd

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(semPlot)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
library(rvest)
source('production/prod_polychoric.R')
```

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
save(cor04, file = "output/images/correlation.RData")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

#------chi2, df------#
fm04<- round(rbind(fm01,fm02,fm03),3)
fm04.1 <- fm04 %>% select(chisq.scaled,df) 
fm04.1$chisq.scaled <- round(x = fm04.1$chisq.scaled,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq.scaled,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

@@

fm.df      <- bind_cols(fm04.1,fm04.2)
fm.df$nobs <- c(nobs(fit1_o),nobs(fit2_o),nobs(fit3_o)) 
fm.df <- data.frame(t(fm.df)); colnames(fm.df) <- c("M1.2","M2.2","M3.2")

#------ merge ------#
tb.fm<- bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>% select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.foot <- paste0("; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
          column_spec(column = 2:13,width = "1cm",width_min = "1.3cm",include_thead = TRUE) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
save(tb.fm01,file = "output/tables/tb.fm01.RData")

save(tb.fm,file = "output/tables/tb.fm.RData")
save(fm.df,file = "output/tables/fm.df.RData")
save(tb.load,file = "output/tables/tb.load.RData")

@@

dir.create("output/images")

semPaths(plot01,
         style = "lisrel",
         fade=FALSE,
         edge.color = "black",
         nCharNodes = 0,
         curvePivot = FALSE,
         curve = 2,
         rotation = 4,
         layout = "tree3",
         cardinal = "lat cov",
         legend.cex = 0.6,
         label.cex =1,
         reorder = FALSE,
         nodeNames = nodeNames,
         nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"),
         label.font = 6,
         edge.label.font= 1,
         asize = 3, #arrow size
         edge.width =1,
         sizeMan=5,
         sizeLat = 10,
         filetype ="png",
         width = 12,
         height= 10,
         filename = "output/images/meas01")
```

@@

```{r}
library(ggplot2)
library(reshape2)
library(sjPlot)
library(dplyr)

#install.packages("cowplot")
library(cowplot)

dat_merit <- dat04 %>% select("a.Effort"=perc_effort,"a.Talent"=perc_talent, "a.Rich Parents"=perc_wpart, "a.Contacts"=perc_netw, "b.Effort"=pref_effort,"b.Talent"=pref_talent,"b.Rich Parents"=pref_wpart, "b.Contacts"=pref_netw)

plotlikert<-plot_likert(dat_merit, c(1,1,1,1,2,2,2,2),
            groups.titles = c("Perceptions","Preferences"),
            geom.colors ="PuBu", 
            axis.labels=c("Effort","Talent","Rich Parents","Contacts"),
            catcount = 4,
            cat.neutral = 3, 
            grid.range  =  c ( 1.2 , 1.4 ),
            values  =  "sum.outside",
            reverse.scale=TRUE)
plotlikert

ggsave(plotlikert,filename = "output/images/plotlikert.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

@@

>>>>

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(semPlot)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
library(rvest)
library(sjlabelled)
source('production/prod_polychoric.R')
```

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

#------chi2, df------#
fm04<- round(rbind(fm01,fm02,fm03),3)
fm04.1 <- fm04 %>% select(chisq.scaled,df) 
fm04.1$chisq.scaled <- round(x = fm04.1$chisq.scaled,digits = 2)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq.scaled,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

@@

fm.df      <- bind_cols(fm04.1,fm04.2)
fm.df$nobs <- c(nobs(fit1_o),nobs(fit2_o),nobs(fit3_o)) 
fm.df <- data.frame(t(fm.df)); colnames(fm.df) <- c("M1.1","M2.1","M3.1")
#------ merge ------#
tb.fm<- bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>% select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.foot <- paste0("; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
          column_spec(column = 2:13,width = "1cm",width_min = "1.3cm",include_thead = TRUE) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
save(tb.fm01,file = "output/tables/tb.fm01.RData")
```

@@

dir.create("output/images")
semPaths(plot01,
         style = "lisrel",
         fade=FALSE,
         edge.color = "black",
         nCharNodes = 0,
         curvePivot = FALSE,
         curve = 2,
         rotation = 4,
         layout = "tree3",
         cardinal = "lat cov",
         legend.cex = 0.6,
         label.cex =1,
         reorder = FALSE,
         nodeNames = nodeNames,
         nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"),
         label.font = 6,
         edge.label.font= 1,
         asize = 3, #arrow size
         edge.width =1,
         sizeMan=5,
         sizeLat = 10,
         filetype ="png",
         width = 12,
         height= 10,
         filename = "output/images/meas01")

@@

# Anexo 1: Sample

```{r}
load(file = "input/data/original/issp2019CL.RData")
w01 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola1.sav",verbose = F)
```

```{r}
GS<- c("CERRILLOS",
"CERRO NAVIA",
"CONCHALÍ",
"EL BOSQUE",
"ESTACIÓN CENTRAL",
"HUECHURABA",
"INDEPENDENCIA",
"LA CISTERNA",
"LA FLORIDA",
"LA GRANJA",
"LA PINTANA",
"LA REINA",
"LAS CONDES",
"LO BARNECHEA",
"LO ESPEJO",
"LO PRADO",
"MACUL",
"MAIPÚ",
"ÑUÑOA",
"PEDRO AGUIRRE CERDA",
"PEÑALOLEN",
"PROVIDENCIA",
"PUDAHUEL",
"PUENTE ALTO",
"QUILICURA",
"QUINTA NORMAL",
"RECOLETA",
"RENCA",
"SAN BERNARDO",
"SAN JOAQUÍN",
"SAN MIGUEL",
"SAN RAMÓN",
"SANTIAGO",
"VITACURA")

cl19$COMUNA <- toupper(as_character(cl19$COMUNA))

# cl19$DS_P1 # 1= hombre, 2= mujer
# cl19$DS_P2_EXACTA  
# cl19$DS_P4

cep1 <- cl19 %>% 
  select(COMUNA,DS_P1,DS_P2_EXACTA,DS_P4, FACTOR) %>% 
  filter(COMUNA %in% GS)
```

```{r}
cep1$edad_cat<- as.numeric(cep1$DS_P2_EXACTA) # Edad
cep1$edad_cat[cep1$edad_cat %in%c(18:24)] <- 1   #"18 a 24"
cep1$edad_cat[cep1$edad_cat %in%c(25:34)] <- 2 # "25 a 34"
cep1$edad_cat[cep1$edad_cat %in%c(35:44)] <- 3 # "35 a 44"
cep1$edad_cat[cep1$edad_cat %in%c(45:54)] <- 4 # "45 a 54"
cep1$edad_cat[cep1$edad_cat >=  55]       <- 5 # "55 o más"

cep1$educ <- cep1$DS_P4 # Educación
cep1$educ <- as_numeric(cep1$educ)
cep1$educ <- as.numeric(cep1$educ)
cep1$educ[cep1$educ %in%c(88,99)] <- NA

cep1$educ <- recode(cep1$educ, "0" = "1" , "1"="1", "2" = "1", "3"="2","4"="2", "5"="3","6"="3", "7" = "3", "8"="4" , "9"="4"   )

cep1$sexo <- as.numeric(cep1$DS_P1) # 1= hombre, 2= mujer

@@

```{r}

# Gender

cep1$Hombres<-ifelse(cep1$sexo==1,100,0)
cep1$Mujeres<-ifelse(cep1$sexo==2,100,0)
w01$Hombres<-ifelse(w01$sexo==1,100,0)
w01$Mujeres<-ifelse(w01$sexo==2,100,0)

cep1$ed_a<-ifelse(cep1$edad_cat==1,100,0)
cep1$ed_b<-ifelse(cep1$edad_cat==2,100,0)
cep1$ed_c<-ifelse(cep1$edad_cat==3,100,0)
cep1$ed_d<-ifelse(cep1$edad_cat==4,100,0)
cep1$ed_e<-ifelse(cep1$edad_cat==5,100,0)
w01$ed_a<-ifelse(w01$edad==1,100,0)
w01$ed_b<-ifelse(w01$edad==2,100,0)
w01$ed_c<-ifelse(w01$edad==3,100,0)
w01$ed_d<-ifelse(w01$edad==4,100,0)
w01$ed_e<-ifelse(w01$edad==5,100,0)

cep1$educ_a<-ifelse(cep1$educ==1,100,0)
cep1$educ_b<-ifelse(cep1$educ==2,100,0)
cep1$educ_c<-ifelse(cep1$educ==3,100,0)
cep1$educ_d<-ifelse(cep1$educ==4,100,0)
w01$educ_a<-ifelse(w01$educat==1,100,0)
w01$educ_b<-ifelse(w01$educat==2,100,0)
w01$educ_c<-ifelse(w01$educat==3,100,0)
w01$educ_d<-ifelse(w01$educat==4,100,0)

Men<-round(c(mean(w01$Hombres, na.rm = T), weighted.mean(cep1$Hombres,cep1$FACTOR, na.rm = T)),digits = 2)
Women<-round(c(mean(w01$Mujeres, na.rm = T), weighted.mean(cep1$Mujeres,cep1$FACTOR, na.rm = T)),digits = 2)

years.18.to.24<-round(c(mean(w01$ed_a, na.rm = T), weighted.mean(cep1$ed_a,cep1$FACTOR, na.rm = T)),digits = 2)
years.25.to.34<-round(c(mean(w01$ed_b, na.rm = T), weighted.mean(cep1$ed_b,cep1$FACTOR, na.rm = T)),digits = 2)
years.35.to.44<-round(c(mean(w01$ed_c, na.rm = T), weighted.mean(cep1$ed_c,cep1$FACTOR, na.rm = T)),digits = 2)
years.45.to.54<-round(c(mean(w01$ed_d, na.rm = T), weighted.mean(cep1$ed_d,cep1$FACTOR, na.rm = T)),digits = 2)
years.55.or.more<-round(c(mean(w01$ed_e, na.rm = T), weighted.mean(cep1$ed_e,cep1$FACTOR, na.rm = T)),digits = 2)

Primary <-round(c(mean(w01$educ_a, na.rm = T), weighted.mean(cep1$educ_a,cep1$FACTOR, na.rm = T)),digits = 2)
Secondary<-round(c(mean(w01$educ_b, na.rm = T), weighted.mean(cep1$educ_b,cep1$FACTOR, na.rm = T)),digits = 2)
Technique<-round(c(mean(w01$educ_c, na.rm = T), weighted.mean(cep1$educ_c,cep1$FACTOR, na.rm = T)),digits = 2)
University<-round(c(mean(w01$educ_d, na.rm = T), weighted.mean(cep1$educ_d,cep1$FACTOR, na.rm = T)),digits = 2)

sample_cep<- rbind("__Gender__",Men,Women,"__Age__",years.18.to.24,years.25.to.34,years.35.to.44,years.45.to.54,years.55.or.more, "__Education__", Primary, Secondary, Technique, University)

cnames <- c("Sample", "CEP") 
knitr::kable(sample_cep, digits = 0, format = "markdown",col.names = cnames)

# Anexo 2: Fiability

```{r}
lav.mod.1 <- 'perc_merit =~ perc_effort+perc_talent
perc_nmerit=~perc_wpart +perc_netw
pref_merit =~ pref_effort+pref_talent
pref_nmerit=~pref_wpart +pref_netw'

cor01a<-polychoric(dat01)
cor02a<-polychoric(dat02)
cor03a<-polychoric(dat03)
cor04a <-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))

#Omega for group
lav.jen.1<- cfa(lav.mod.1,sample.cov=cor01a$rho,sample.nobs=500,orthogonal=TRUE,std.lv=TRUE) # Total sample
lav.jen.2<- cfa(lav.mod.1,sample.cov=cor02a$rho,sample.nobs=500,orthogonal=TRUE,std.lv=TRUE) # Total sample
lav.jen.3<- cfa(lav.mod.1,sample.cov=cor03a$rho,sample.nobs=500,orthogonal=TRUE,std.lv=TRUE) # Total sample
lav.jen.4<- cfa(lav.mod.1,sample.cov=cor04a$rho,sample.nobs=500,orthogonal=TRUE,std.lv=TRUE) # Total sample

o1 <- omegaFromSem(lav.jen.1,cor04a$rho, plot = F)
o2<-omegaFromSem(lav.jen.2,cor04a$rho, plot = F)
o3<-omegaFromSem(lav.jen.3,cor04a$rho, plot = F)
o4<-omegaFromSem(lav.jen.4,cor04a$rho, plot = F)

Group_1 <- c(o1$omega.group$total)
Group_2 <- c(o2$omega.group$total)
Group_3 <- c(o3$omega.group$total)
Total_sample <- c(o4$omega.group$total)

Omega<- rbind(Group_1,Group_2,Group_3,Total_sample)

cnames <- c("Perception Meritocratic","Perception Non Meritocratic", "Preference Meritocratic","Preference Non Meritocratic")
knitr::kable(Omega, format = "markdown",digits = 2, col.names = cnames)
